Demographics: The Sound of Teaching Music 2

### 2022-06-23 experiment-1/analysis/demographics/questionnaire.Rmd
export r chunks as R scripts
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update demographic data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# change some colnames
colnames(dt)[2] <- "SubNr"
colnames(dt)[3] <- "Age"
colnames(dt)[4] <- "Gender"
colnames(dt)[7] <- "Handedness"

@@

# extract the total number of years of training in piano (input manually based on the original csv file)
dt$PianoTotalPractice <- c(14, 20, 27, 21, 10, 16, 9, 13, 25, 14, 13, 11, 6, 4, 6, 8, 21, 15, 18, 7, 11, 12, 12, 18, 12, 5, 5, 10, 16, 10, 8, 22, 10, 5, 4, 14)

@@

## Descriptive stats for included participants
- Number of included participants: `r nrow(dt_included)` (mean age: `r round(mean(dt_included$Age), 2)`, sd: `r round(sd(dt_included$Age), 2)`)
- Male: `r nrow(dt_included[Gender == "Male"])` (mean age: `r round(mean(dt_included[Gender == "Male"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Male"]$Age), 2)`)
- Female: `r nrow(dt_included[Gender == "Female"])` (mean age: `r round(mean(dt_included[Gender == "Female"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Female"]$Age), 2)`)
- Average training years: `r round(mean(dt_included$PianoTotalPractice), 2)` years
- Handedness: Right (`r nrow(dt_included[Handedness == "Right"])`), Left (`r nrow(dt_included[Handedness == "Left"])`), Both (`r nrow(dt_included[Handedness == "Both"])`)

## Some descriptive questions
1. Did you try to perform differently when you are asked to play as a teacher during the experiment? If so, please describe how you changed your performance?

@@

>>>>

# change some colnames
colnames(dt)[2] <- "SubNr"
colnames(dt)[3] <- "Age"
colnames(dt)[4] <- "Gender"
colnames(dt)[7] <- "Handedness"
colnames(dt)[18] <- "TeachingMusic"

@@

# extract the total number of years of training in piano (input manually based on the original csv file)
dt$PianoTotalPractice <- c(14, 20, 27, 21, 10, 16, 9, 13, 25, 14, 13, 11, 6, 4, 6, 8, 21, 15, 18, 7, 11, 12, 12, 18, 12, 5, 5, 10, 16, 10, 8, 22, 10, 5, 4, 14)
dt$TeachingPianoYears <- c(NA, 4, NA, 12, NA, 3, NA, NA, 3, NA, NA, NA, NA, NA, 5, NA, 5, NA, 0.17, NA, NA, NA, NA, 0.17, NA, NA, NA, NA, 2, NA, NA, 0.5, NA, NA, NA, NA)
dt$TeachingPiano <- "No"
dt[!is.na(TeachingPianoYears)]$TeachingPiano <- "Yes"

@@

## Descriptive stats for included participants

- Number of included participants: `r nrow(dt_included)` (mean age: `r round(mean(dt_included$Age), 2)`, sd: `r round(sd(dt_included$Age), 2)`)
- Male: `r nrow(dt_included[Gender == "Male"])` (mean age: `r round(mean(dt_included[Gender == "Male"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Male"]$Age), 2)`)
- Female: `r nrow(dt_included[Gender == "Female"])` (mean age: `r round(mean(dt_included[Gender == "Female"]$Age), 2)`, sd: `r round(sd(dt_included[Gender == "Female"]$Age), 2)`)
- Average training years: `r round(mean(dt_included$PianoTotalPractice), 2)` years
- Handedness: Right (`r nrow(dt_included[Handedness == "Right"])`), Left (`r nrow(dt_included[Handedness == "Left"])`), Both (`r nrow(dt_included[Handedness == "Both"])`)
- Teaching experience (any instrument): Yes (`r nrow(dt_included[TeachingMusic == "Yes"])`), No (`r nrow(dt_included[TeachingMusic == "No"])`)
- Teaching experience (piano): Yes (`r nrow(dt_included[TeachingPiano == "Yes"])`, mean years of teaching: `r round( mean(dt_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)`, sd: `r round(sd(dt_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)`), No (`r nrow(dt_included[TeachingPiano == "No"])`)

## Some descriptive questions

1. Did you try to perform differently when you are asked to play as a teacher during the experiment? If so, please describe how you changed your performance?

@@

```{r export, include = FALSE}
knitr::purl("questionnaire.Rmd")
```

### 2022-06-23 experiment-2/analysis/demographics/questionnaire.Rmd
export Rmd as R
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
update demographic data
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# change some colnames
colnames(dt_2)[2] <- "SubNr"
colnames(dt_2)[3] <- "Age"
colnames(dt_2)[4] <- "Gender"
colnames(dt_2)[7] <- "Handedness"
colnames(dt_2)[18] <- "PianoTotalPractice"

# extract the total number of years of training in piano (input manually based on the original csv file)
dt_2$PianoTotalPractice <- c(13, 15, 15, 16, 9, 10, 24, 8, 19, 6, 12, 10, 21, 23, 15, 22, 22, 24, 17, 15, 12)

@@

- Number of included participants: `r nrow(dt_2_included)` (mean age: `r round(mean(dt_2_included$Age), 2)`, sd: `r round(sd(dt_2_included$Age), 2)`)
- Male: `r nrow(dt_2_included[Gender == "Male"])` (mean age: `r round(mean(dt_2_included[Gender == "Male"]$Age), 2)`, sd: `r round(sd(dt_2_included[Gender == "Male"]$Age), 2)`)
- Female: `r nrow(dt_2_included[Gender == "Female"])` (mean age: `r round(mean(dt_2_included[Gender == "Female"]$Age), 2)`, sd: `r round(sd(dt_2_included[Gender == "Female"]$Age), 2)`)
- Average training years: `r round(mean(dt_2_included$PianoTotalPractice), 2)` years
- Handedness: Right (`r nrow(dt_2_included[Handedness == "Right"])`), Left (`r nrow(dt_2_included[Handedness == "Left"])`), Both (`r nrow(dt_2_included[Handedness == "Both"])`)

>>>>

# change some colnames
colnames(dt_2)[2] <- "SubNr"
colnames(dt_2)[3] <- "Age"
colnames(dt_2)[4] <- "Gender"
colnames(dt_2)[7] <- "Handedness"
colnames(dt_2)[18] <- "PianoTotalPractice"
colnames(dt_2)[28] <- "TeachingMusic"

# extract the total number of years of training in piano (input manually based on the original csv file)
dt_2$PianoTotalPractice <- c(13, 15, 15, 16, 9, 10, 24, 8, 19, 6, 12, 10, 21, 23, 15, 22, 22, 24, 17, 15, 12)
dt_2$TeachingPianoYears <- c(NA, 4, NA, 2, NA, NA, NA, NA, 5, NA, NA, NA, 0.5, 9, 11, 2, NA, 8, 2, 1, 1)
dt_2$TeachingPiano <- "No"
dt_2[!is.na(TeachingPianoYears)]$TeachingPiano <- "Yes"

@@

- Number of included participants: `r nrow(dt_2_included)` (mean age: `r round(mean(dt_2_included$Age), 2)`, sd: `r round(sd(dt_2_included$Age), 2)`)
- Male: `r nrow(dt_2_included[Gender == "Male"])` (mean age: `r round(mean(dt_2_included[Gender == "Male"]$Age), 2)`, sd: `r round(sd(dt_2_included[Gender == "Male"]$Age), 2)`)
- Female: `r nrow(dt_2_included[Gender == "Female"])` (mean age: `r round(mean(dt_2_included[Gender == "Female"]$Age), 2)`, sd: `r round(sd(dt_2_included[Gender == "Female"]$Age), 2)`)
- Average training years: `r round(mean(dt_2_included$PianoTotalPractice), 2)` years
- Handedness: Right (`r nrow(dt_2_included[Handedness == "Right"])`), Left (`r nrow(dt_2_included[Handedness == "Left"])`), Both (`r nrow(dt_2_included[Handedness == "Both"])`)
- Teaching experience (any instrument): Yes (`r nrow(dt_2_included[TeachingMusic == "Yes"])`), No (`r nrow(dt_2_included[TeachingMusic == "No"])`)
- Teaching experience (piano): Yes (`r nrow(dt_2_included[TeachingPiano == "Yes"])`, mean years of teaching: `r round( mean(dt_2_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)`, sd: `r round(sd(dt_2_included[TeachingPiano == "Yes"]$TeachingPianoYears), 2)`), No (`r nrow(dt_2_included[TeachingPiano == "No"])`)
